---
title: "Coronavirus"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
 #    vertical_layout: scroll
  #  vertical_layout: fill
---


```{r label = RCode, include = FALSE}
knitr::read_chunk("RCode.R")
```


```{r label = Packages, include = FALSE}
```

```{r label = Parameters}
```


```{r label = PakCoronaData}
```

Pakistan
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------

### Cumulative Number of Confirmed Cases

```{r label = PakConfirmedPlot1}
```

### Cumulative Number of Active Cases

```{r label = PakActivePlot1}
```


### Number of New Cases

```{r label = PakNewPlot1}
```



Row
----------------------------------------------------------------------

### Number of Recovered Cases

```{r label = PakRecoveredPlot1}
```


### Number of Deaths

```{r label = PakDeathsPlot1}
```

### Data for COVID-19

```{r label = PakCoronaData1}
```


Punjab
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------


Sindh
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------


KPK
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------



Balochistan
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------


ICT
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------



Gilgit Baltistan
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------


AJK
======================================================================

Row
----------------------------------------------------------------------
  
### Confirmed {.value-box}

```{r label = PakConfirmed}
```

### Active {.value-box}

```{r label = PakActive}
```

### Recovered {.value-box}

```{r label = PakRecovered}
```


### Death {.value-box}

```{r label = PakDeaths}
```


Row
----------------------------------------------------------------------

